Semantic Adversarial Autoencoder for Zero-Shot Learning

### 2017-12-13 doc/paper.tex
Revised paper.
Revise paper

@@

Inspired by these models, we propose the model of Semantic adversarial autoencoder (SAAE). In this model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features. Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples. Two types of models that use different priors are investigated. In one type of the model, the prior is the Gaussian noise prior, and in the other type the semantic representation itself is used as the prior.

@@

	The optimization problem for the autoencoder and the generator is
	\begin{align}
		\min_{W^e} \; f_g,
	\end{align}
	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
	\begin{align}
		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
	\end{align}
	while the parameters of the generator ($W^e, \bb{b}^e, W^d, \bb{b}^d$) are held constant.

@@

	We also check whether adding GAN to the original architecture of SAE will change the performance of SAE. We solve the following optimization problem,
	\begin{align}
		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G_{\textrm{SAE}}(\bb{x})) ) + L_{\textrm{SAE}} \;\right],
	\end{align}
	where
	\begin{align}
		G_{\textrm{SAE}}(\bb{x}) = W \bb{x}.
	\end{align}

@@

By adding GAN on top of the SAE, we find that on the AwA dataset it improves the accuracy, but on the CUB dataset it does not. For the standard ZSL on the AwA dataset, in which GAN makes the most significant improvement, we conduct more detailed experiments to check how accuracy changes by using different coefficients for the GAN. The results are shown in Table \ref{tab:SAEGAN}. We observe that with suitable coefficient, GAN slightly improves the accuracy, but if the coefficient of GAN is too large, it harms the performance.

>>>>

\usepackage{courier}	% for \texttt{}

@@

Inspired by these models, we propose the model of semantic adversarial autoencoder (SAAE)%
\footnote{The code is available on \texttt{https://github.com/yuhsianglin/10707DL\_proj}.}%
. In this model, we have an encoder that projects a visual feature vector into the semantic space and a decoder that decodes and reconstructs the original visual features. Besides, we incorporates a discriminator as in \cite{makhzani2015adversarial} to ensure that generating from any part of prior space results in meaningful samples. Two types of models that use different priors are investigated. In one type of the model, the prior is the Gaussian noise prior, and in the other type the semantic representation itself is used as the prior.

@@

	The optimization problem for the autoencoder and the generator is
	\begin{align}
		\min_{W^e} \; f_g,
	\end{align}
	while the parameters of the discriminator ($W^1, \bb{b}^1, \bb{w}^2, b^2$) are held constant. The optimization problem for the discriminator is
	\begin{align}
		\min_{W^1, \bb{b}^1, \bb{w}^2, b^2} \; f_d,
	\end{align}
	while the parameters of the generator ($W^e$) are held constant.

@@

	We also check whether adding GAN to the original architecture of SAE will change the performance of SAE. We solve the following optimization problem,
	\begin{align}
		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \lambda_{\textrm{GAN}} \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \lambda_{\textrm{GAN}} \log( 1 - D(G_{\textrm{SAE}}(\bb{x})) ) + \lambda_{\textrm{SAE}} L_{\textrm{SAE}} \;\right],
	\end{align}
	where
	\begin{align}
		G_{\textrm{SAE}}(\bb{x}) = W \bb{x},
	\end{align}
	and $\lambda_{\textrm{GAN}}$ and $\lambda_{\textrm{SAE}}$ are introduced to specify the relative importance of the GAN and SAE parts in the optimization objective.

@@

By adding GAN on top of the SAE, we find that on the AwA dataset it improves the accuracy, but on the CUB dataset it does not. For the standard ZSL on the AwA dataset, in which GAN makes the most significant improvement, we conduct more detailed experiments to check how accuracy changes by using different coefficients $\lambda_{\textrm{GAN}}$ for the GAN while keeping $\lambda_{\textrm{SAE}}$ fixed. The results are shown in Table \ref{tab:SAEGAN}. We observe that with suitable coefficient, GAN slightly improves the accuracy, but if the coefficient of GAN is too large, it harms the performance.
